\section{Source Installation}
There are several required elements to use the srouce installation.

\begin{itemize}
\item LLVM - obtain version 1.5 from www.llvm.org
\item LLVM cfrontend - obtain version 1.5 from www.llvm.org
\item ant - obtain 1.6.X from ant.apach.org, 1.7.X is untested.
\item antlr.jar - obtain 2.7.3 or later from www.antlr.org
\item java-getopt.jar - obtain version 1.11 or later from \\
http://www.urbanophile.com/arenn/hacking/download.html
\item Java - obtain from java.sun.com (tested with 1.4.2)
\item Python - obtain from www.python.org
\item gcc, unix environment, etc.
\item Graphviz (dotty and friends) from www.graphviz.org can be useful, but is not required.
\end{itemize}

First obtain LLVM and compile LLVM.  The following works on RHEL 3.0u5
with tcsh, and detailed instructions are available on www.llvm.org.
If you prefer bash, use the proper commands for setting variables
(e.g., export BLAH=SOME\_VALUE and export
PATH=\$PATH:NEW\_PATH\_VALUE, etc.).

\begin{verbatim}
> tar xzf llvm-1.5.tar.gz
> tar xzf cfrontend-1.5.i686-redhat-linux-gnu.tar.gz

#
# must have java
#
> which java
>
> setenv TOP `pwd`

> cd cfrontend/x86/
> ./fixheaders
> cd ../..

> set path = ( $path $TOP/cfrontend/x86/llvm-gcc/bin/ )

> mkdir llvm-obj
> cd llvm-obj

> ../llvm/configure
> make
# wait 

> cd ..
> set path = ( $path $TOP/llvm-obj/Debug/bin/ )

\end{verbatim}

Now LLVM should be built.  This will build the Debug version of LLVM
and anything else may not work without changing some of the scripts
provided.

Next, unpack the Trident files and execute the
following:\footnote{This is a continuation of the above and uses the
  same TOP variable.  It could be modified to support a different
  location than parallel with LLVM.}

\begin{verbatim}
> tar xzf dist.tgz

# build llv
# 
> cd trident/llv-src
> ./mkconf.sh --src=$TOP/llvm
> ./configure --with-llvmsrc=$TOP/llvm/ --with-llvmobj=$TOP/llvm-obj/

> make
> cp Debug/bin/llv ../bin
> strip ../bin/llv
> chmod a+x ../bin/llv

> cd ..

# copy jars to $TRIDENT_TOP/lib
#
> cp somewhere/antlr.jar lib/
> cp somewhere/java-getopt.jar lib/
\end{verbatim}

Next, compile Trident.  This requires ant, python, java and the jars
just added to the above lib directory.  Modify your Java classpath to
include the jars.

\begin{verbatim}
> cd trident-src/fp
> ant dist
> cd ../..
> cp trident-src/dist/lib/Trident.jar lib/

> set path = ($path $TOP/trident/bin )

> setenv TRIDENT_TOP $TOP/trident
\end{verbatim}

Now, you should have all the tools necessary to run Trident.  Test the 
compiler using the following:

\begin{verbatim}
cd examples/conditional
tcc -t vhdl conditional_a.c run

less conditional_a.vhd
\end{verbatim}

This will generate a VHDL file for the conditional\_a.c example.  The
output of the compiler is extremely verbose and needs to be cleaned up.
Serious errors will cause the compiler to exit, the many warnings can
usually be safely ignored.


